A protocol and event-sourced database for decentralized user-siloed data

### 2019-09-27 draft.tex
updates
Signed-off-by: andrew <andrew@textile.io>
more
Signed-off-by: andrew <andrew@textile.io>

\title[A protocol and event-sourced database for decentralized user-siloed data]{A protocol and event-sourced database for decentralized user-siloed data}
\author{Pick}
\author{Farmer}
\author{Sutula}
\affiliation{www.textile.io} \email{research@textile.io}
\author{?Others?}
\affiliation{other?} \email{research@textile.io}
\author{Hill}
\affiliation{www.textile.io} \email{contact@textile.io}

@@

A view Model is generally defined by custom update logic (i.e., a Reducer), a (possibly ORM\footnote{Object-relational mapping}-based) view Store for persistence, an Event Bus (or Broadcaster) for notifying downstream consumers, and a set of query/\emph{Resolver} \cite{ereminReduxInspiredBackend2019} functions. In practice, a view Model may \emph{also} wrap the Event Creator application logic that is used to generate upstream Events. This provides an intuitive, singular access point to the \emph{local} system, while also leaving room for updates via \emph{external} peer-events. In practice, the Store is a lightweight interface that can be implemented by one of many database management systems (\ref{appx:DBMS}).

>>>>

\title[A protocol and event-sourced database for decentralized user-siloed data]{A protocol and event-sourced database for decentralized user-siloed data}
\author{Pick}
\author{Farmer}
\author{Sutula}
\affiliation{www.textile.io} \email{research@textile.io}
\author{?Gozalishivili others?}
\affiliation{other?} \email{research@textile.io}
\author{Hill}
\affiliation{www.textile.io} \email{contact@textile.io}

@@

A view Model is generally defined by custom update logic (i.e., a Reducer), a (possibly ORM\footnote{Object-relational mapping}-based) view Store for persistence, an Event Bus (or Broadcaster) for notifying downstream consumers, and a set of query/\emph{Resolver} \cite{ereminReduxInspiredBackend2019} functions. In practice, a view Model may \emph{also} wrap the Event Creator application logic that is used to generate upstream Events. This provides an intuitive, singular access point to the \emph{local} system, while also leaving room for updates via \emph{external} peer-events. In practice, the Store is a lightweight interface that can be implemented by one of many database management systems (\ref{appx:DBMS}) providing end users/developers the greatest flexibility.
